\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

% Contact Info
\begin{flushright}
Miguel Rodriguez \\
915-234-5678 \\
El Paso, Texas
\end{flushright}

\vspace*{-0.5cm}

% Objective
\textbf{Forklift Operator and Warehouse Supervisor} - Experienced in operating forklifts and managing warehouse operations with a strong focus on safety and efficiency.

\vspace*{1cm}

\section{Skills}
\resumeSubHeadingListStart
    \resumeItemListStart
      \resumeItem{\textbf{Technical Skills:} Forklift operation (sit-down and stand-up), Pallet jack, MIG welding, Power tools (drills, impact drivers, grinders), Hand tools, Overhead crane, RF scanner, Inventory management systems}
      \resumeItem{\textbf{Certifications \& Licenses:} Forklift Certification (valid through Dec 2025), OSHA 10-Hour Safety, First Aid/CPR, CDL Class B}
      \resumeItem{\textbf{Core Competencies:} Safety compliance, Quality control, Team leadership, Problem-solving, Attention to detail, Physical stamina (lift 50+ lbs), Reliable attendance}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace*{1cm}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {El Paso Community College}{May 2019}
    {Certificate in Welding Technology}{El Paso, TX}
\resumeSubHeadingListEnd

\vspace{-15pt}

\section{Training \& Certifications}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Forklift Operator Certification} - SafetyFirst Training, Valid through December 2025}
    \resumeItem{\textbf{OSHA 10-Hour Construction Safety} - OSHA, Completed March 2023}
    \resumeItem{\textbf{CDL Class A License} - Texas DMV, Valid through June 2026, No restrictions}
    \resumeItem{\textbf{First Aid/CPR/AED} - American Red Cross, Valid through January 2026}
\resumeSubHeadingListEnd

\vspace{-16pt}

\section{Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {ABC Manufacturing}{January 2020 - Present}
    {Forklift Operator and Supervisor}{El Paso, Texas}
    \resumeItemListStart
      \resumeItem{Supervised a team of warehouse operators in daily operations.}
      \resumeItem{Ensured compliance with safety regulations and company policies.}
      \resumeItem{Operated forklifts to move heavy materials with precision and efficiency.}
      \resumeItem{Managed inventory levels, ensuring accurate stock records and minimizing waste.}
    \resumeItemListEnd

  \resumeSubheading
    {XYZ Electronics}{June 2018 - December 2019}
    {Forklift Operator}{El Paso, Texas}
    \resumeItemListStart
      \resumeItem{Operated forklifts to move electronic components and assemblies in a fast-paced environment.}
      \resumeItem{Assisted in the loading and unloading of trucks and shipping containers.}
      \resumeItem{Completed training on safety procedures and emergency response protocols.}
    \resumeItemListEnd

  \resumeSubheading
    {DEF Construction}{June 2017 - May 2018}
    {Forklift Operator Trainee}{El Paso, Texas}
    \resumeItemListStart
      \resumeItem{Assisted experienced operators in learning and applying forklift operation techniques.}
      \resumeItem{Participated in safety training sessions to enhance awareness of potential hazards.}
      \resumeItem{Completed initial training on forklift operation and basic warehouse management tasks.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}